% !TEX program = latexmk
% !TEX options = -synctex=1 -file-line-error -halt-on-error -xelatex -outdir="%OUTDIR%" "%DOC%"

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{GALILEU}{KIM}{ \urlstyle{same}\href{http://kimgalileu.com}{kimgalileu.com}\\
\href{mailto:galileukim@gmail.com}{galileukim@gmail.com} | 609.455.2983
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EDUCATION
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \section{Education}
    
    \subsection{Princeton University}
    \descript{Ph.D. in Political Science}
    \location{Expected May 2021 | Princeton, US}
    GPA: 3.77 / 4.0
    \sectionsep
    
    \subsection{University of Pennsylvania}
    \descript{B.A. in Political Science and Economics}
    \location{2009 - 2013 | Philadelphia, US}
    % College of Engineering \\
    GPA: 3.85/ 4.0\\
    Summa cum laude, Phi Beta Kappa
    \sectionsep
    
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     SKILLS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \section{Skills}
    \subsection{Programming}
    R \textbullet{} Python \textbullet{} SQL \\
    ArcGIS \textbullet{} Spark
    
    \subsection{Technology}
    GitHub \textbullet{} DataBricks \textbullet{} Linux \\
    \sectionsep
    
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     AWARDS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \section{Grants}
    Lassen Fellowship for Latin American Scholars\\
    Princeton Institute for International and Regional Studies\\
    Program for Latin American Studies\\
    Mahmoud Bobst Center for Peace and Justice
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     COURSEWORK
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \section{Coursework}
    \subsection{Graduate}
    Comparative Political Economy of Development\\
    Quantitative Analysis I/II/III/IV\\
    Latin American Politics\\
    Clientelism and Redistributive Politics
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     Societies
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \section{Societies}
    Brazil Lab\\
    Program in Political Economy\\
    Program for Latin American Studies\\
    Penn Brazil Club\\
    \sectionsep
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     LINKS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \section{Links}
    Github:// \href{https://github.com/galileukim}{\bf galileukim} \\
    LinkedIn://  \href{https://www.linkedin.com/in/galileu-kim}{\bf galileu-kim} \\
    \sectionsep
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     COLUMN TWO
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hfill
    \end{minipage} 
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{ELOGROUP}
\descript{| Data Scientist }
\location{2019 - present | Brasilia, Brazil}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Partnership with the Brazilian Department of Labor to restructure national employment system (SINE) and create a job matching algorithm for over 60 million formal workers in Brazil.
\item Partnership with the Brazilian Ministry of Finance to create a detection algorithm and triage system for irregular payrolls in the federal bureaucracy. Savings of over 50 million BRL every month.
\end{tightemize}
\sectionsep

\runsubsection{INSTITUTO DEL PERU}
\descript{| Research member }
\location{2013 – 2015 | Lima, Peru}
\begin{tightemize}
\item Solo-authored study on the diffusion of agricultural technologies in Peru between 1994 and 2012, funded by the Food and Agriculture Organization (FAO) and the Consorcio de Investigación Económica y Social (CIES).
\item Comparative study of the impact of mining and improvements in road infrastructure on the development of the Peruvian Andes, with Richard Webb and Giovanni Bonfiglio.
\end{tightemize}
\sectionsep

\runsubsection{Princeton University}
\descript{| Assistant Instructor }
\location{2015 - 2017 | Princeton, US}
\begin{tightemize}
\item Instructor for 250+ students for intro and advanced courses on quantitative social sciences courses, with lectures on causal inference and statistical theory in programming language R.
\item Instructor for 80+ students for introductory course on comparative politics, with emphasis on the political economy of development, welfare states, and state capacity in Latin America.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Government through Patronage: Bargaining for Education in Brazil}
\descript{| Solo}
\begin{tightemize}
\item Hierarchical linear model estimation of the effect of teacher and school principal turnover on student learning in municipal public schools.
\item Assess how patronage networks leave educational staff vulnerable to turnover, as mayors exchange public sector jobs with brokers.
\item In-situ interviews with educational staff and local political actors; statistical analysis of large-scale administrative data on student test scores and bureaucratic careers. 
\end{tightemize}
\sectionsep

\runsubsection{Are anti-corruption audits effective? Evidence from Brazil }
\descript{| Co-Authored with Romain Ferrali}
\begin{tightemize}
\item Program evaluation of the Brazilian Comptroller General's (CGU) municipal anti-corruption audits program.
\item Audits program ineffective at removing corrupt bureaucrats from public office, but better local regulatory environments are effective at reducing corruption.
\end{tightemize}
\sectionsep

\end{minipage} 

\end{document}  \documentclass[]{article}
