% !TEX program = latexmk
% !TEX options = -synctex=1 -file-line-error -halt-on-error -xelatex -outdir="%OUTDIR%" "%DOC%"

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{GALILEU}{KIM}{ \urlstyle{same}\href{http://kimgalileu.com}{kimgalileu.com}\\
\href{mailto:galileukim@gmail.com}{galileukim@gmail.com} | 609.455.2983
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\textbf{Princeton University}
Ph.D. in Political Science\\
\location{Expected May 2021}
GPA: 3.77 / 4.0
\sectionsep
    
\textbf{University of Pennsylvania}\\
B.A. in Political Science and Economics\\
\location{2009 - 13}
GPA: 3.85/ 4.0\\
Summa cum laude, Phi Beta Kappa
\sectionsep
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{ELOGROUP}
\descript{| Data Scientist }
\location{2019 - present | Brasilia, Brazil}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{itemize}
\item Restructure national employment system (SINE) and create a job matching algorithm for over 60 million formal workers in Brazil, in partnership with the Brazilian Department of Labor.
\item Create a detection algorithm and triage system for irregular payrolls in the federal bureaucracy, in partnership with the Ministry of Finance. Savings of over 50 million BRL every month.
\end{itemize}
\sectionsep

\runsubsection{Princeton University}
\descript{| Assistant Instructor }
\location{2015 - 2017 | Princeton, US}
\begin{tightemize}
\item Instructor for 250+ students for intro and advanced courses on quantitative social sciences courses, with lectures on causal inference and statistical theory in programming language R.
\item Instructor for 80+ students for introductory course on comparative politics, with emphasis on the political economy of development, welfare states, and state capacity in Latin America.
\end{tightemize}
\sectionsep


\runsubsection{INSTITUTO DEL PERU}
\descript{| Research member }
\location{2013 – 2015 | Lima, Peru}
\begin{tightemize}
\item Solo-authored study on the diffusion of agricultural technologies in Peru between 1994 and 2012, funded by the Food and Agriculture Organization (FAO) and the Consorcio de Investigación Económica y Social (CIES).
\item Comparative study of the impact of mining and improvements in road infrastructure on the development of the Peruvian Andes, with Richard Webb and Giovanni Bonfiglio.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Government through Patronage: Bargaining for Education}
\descript{| Solo}
\begin{tightemize}
    \item Hierarchical linear model estimation of the effect of teacher and school principal turnover on student learning in municipal public schools.
    \item In-situ interviews with educational staff and local political actors; statistical analysis of large-scale administrative data on student test scores and bureaucratic careers. 
\end{tightemize}
\sectionsep

\runsubsection{Are anti-corruption audits effective? Evidence from Brazil }
\descript{| with Romain Ferrali}
\begin{tightemize}
    \item Analyze the effects of anti-corruption audits on the career choices of 275 thousand municipal bureaucrats in Brazil from 2006 to 2015.
    \item Audits program ineffective at removing corrupt bureaucrats from public office, but better local regulatory environments are effective at reducing corruption.
\end{tightemize}
\sectionsep

\runsubsection{Corporate Interests and Campaign Donations in Brazilian Municipalities}
\descript{| with James Mao}
\begin{tightemize}
    \item Model and assess efficiency of the campaign donations of over 25 thousand companies to political candidates in municipal elections.
    \item Identify that anti-corruption audits attract more corporate donations, suggesting clean-up effects.
\end{tightemize}

    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Skills}
% \subsection{Programming}
R \textbullet{} Python \textbullet{} SQL \textbullet{} \\
ArcGIS \textbullet{} Spark \textbullet{} GitHub \textbullet{} DataBricks \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Grants}
\textbullet{} Lassen Fellowship for Latin American Scholars\\
\textbullet{} Graduat Fellow at the Program for Latin American Studies\\
\textbullet{} Princeton Institute for International and Regional Studies\\
\textbullet{} Mamdouha Bobst Center for Peace and Justice

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Coursework}
\textbullet{} Comparative Political Economy of Development\\
\textbullet{} Quantitative Analysis I/II/III/IV\\
\textbullet{} Latin American Politics\\
\textbullet{} Clientelism and Redistributive Politics

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Societies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Societies}
\textbullet{} Brazil Lab\\
\textbullet{} Program in Political Economy\\
\textbullet{} Program for Latin American Studies\\
\textbullet{} Penn Brazil Club\\
\textbullet{} Phi Beta Kappa
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Links}
Github:// \href{https://github.com/galileukim}{\bf galileukim} \\
LinkedIn://  \href{https://www.linkedin.com/in/leu-kim}{\bf galileu-kim} \\
\sectionsep


\end{document}  \documentclass[]{article}